Exploring Local Explanations of Non-linear Models Using Animated Linear Projections

### 2022-01-14 _paper.rmd
attributuon example revised

```{r shapdistrbd, echo=F, fig.align='center', out.width="60%", fig.cap = "Illustration of the use of SHAP values for a random forest model for salaries of FIFA 2020 players based on nine predictors corresponding to different skills. A star offensive and defensive player, Messi and a defensive player are compared, L. Messi and V van Dijk respectively. Panel (a) is the break-down plot showing one additive feature-attribution. These attributions are sensitive to the order of the features. Panel (b) shows the distribution of attribution for each feature across 25 such permutation of the order of predictors, with the mean displayed as a dot, for each players. Offense and movement are important for Messi but not van Dijk, and conversely, defense and power are important for van Dijk but not Messi."}
knitr::include_graphics("./figures/shap_distr_bd.png")
```

>>>>

```{r shapdistrbd, echo=F, fig.align='center', out.width="60%", fig.cap = "Illustration of the use of SHAP values for a random forest model for salaries of FIFA 2020 players based on nine predictors corresponding to different skills. A star offensive and defensive player are compared, L. Messi and V. van Dijk, respectively. Panel (a) is the break-down plot showing one additive feature-attribution.  Panel (b) shows the distribution of attribution for each feature across 25 permutations of predictors, with the mean displayed as a dot, for each players. Offense and movement are important for Messi but not van Dijk, and conversely, defense and power are important for van Dijk but not Messi."}
knitr::include_graphics("./figures/shap_distr_bd.png")
```

### 2022-01-14 _paper.tex
attributuon example revised

\caption{Illustration of the use of SHAP values for a random forest model for salaries of FIFA 2020 players based on nine predictors corresponding to different skills. A star offensive and defensive player, Messi and a defensive player are compared, L. Messi and V van Dijk respectively. Panel (a) is the break-down plot showing one additive feature-attribution. These attributions are sensitive to the order of the features. Panel (b) shows the distribution of attribution for each feature across 25 such permutation of the order of predictors, with the mean displayed as a dot, for each players. Offense and movement are important for Messi but not van Dijk, and conversely, defense and power are important for van Dijk but not Messi.}\label{fig:shapdistrbd}
\end{figure}

>>>>

\caption{Illustration of the use of SHAP values for a random forest model for salaries of FIFA 2020 players based on nine predictors corresponding to different skills. A star offensive and defensive player are compared, L. Messi and V. van Dijk, respectively. Panel (a) is the break-down plot showing one additive feature-attribution.  Panel (b) shows the distribution of attribution for each feature across 25 permutations of predictors, with the mean displayed as a dot, for each players. Offense and movement are important for Messi but not van Dijk, and conversely, defense and power are important for van Dijk but not Messi.}\label{fig:shapdistrbd}
\end{figure}
